Asymptotic and Numerical Solution for Electrokinetic Flow Around a Spherical Particle

### 2012-09-22 notes/ijnam/ijnam.tex
Fix Irad review.

Note that a $\cU = 0$ solution may exist for a critical $\beta_c > 0$ and $\alpha = 0$, 
if it satisfies:
\begin{equation} \label{eq:crit_beta}
\beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
\end{equation}
Specifically, for $\gamma = 1 + \eps$, where $0 < \eps \ll 1$, $\beta_c = O\pars{\sqrt{\eps}}$:
\begin{equation}
\beta_c \approx \sqrt{-{\cU_1'(1) \eps}/{\cU_3(1)}} = 
 \sqrt{{13440 \eps}/{1129}} \approx 3.45 \sqrt{\eps}.
\end{equation}
That is, there may be a specific nonzero external field for which the particle remains at rest. The physical viability of this solution has yet to be explored.

@@

\begin{figure}[htbp]
    \begin{center}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1000.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1000.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.3981.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.3981.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_1.0000.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_1.0000.eps}
        \caption{Streamlines of the flow for various electric field $\beta$ values: 
        numerical results (left) and analytical approximation (right) for 
        $\gamma = 0.99$.  The steady-state velocity $\cU$ is positive, so the
        ion-exchanger drifts to the right. 
        Note that there is a good correspondence between the numerical
        results and the analytical solution for $\beta < 1$, validating
        the vortex formation. For $\beta \ge 1$, the cubic analytical
        solution does not match the numerical results, due
        to the influence of higher order nonlinear terms in the  solution.
        }
    \label{fig:Vortex}
    \end{center}
\end{figure}

>>>>

Observe that a $\cU = 0$ solution may exist for a critical $\beta_c > 0$ and $\alpha = 0$, 
if it satisfies:
\begin{equation} \label{eq:crit_beta}
\beta_c^2 = -\frac{\cU_1(\gamma)}{\cU_3(\gamma)}.
\end{equation}
Specifically, for $\gamma = 1 + \eps$, where $0 < \eps \ll 1$, $\beta_c = O\pars{\sqrt{\eps}}$:
\begin{equation}
\beta_c \approx \sqrt{-{\cU_1'(1) \eps}/{\cU_3(1)}} = 
 \sqrt{{13440 \eps}/{1129}} \approx 3.45 \sqrt{\eps}.
\end{equation}
That is, there may be a specific nonzero external field for which the particle remains at rest. The physical viability of this solution has yet to be explored.

@@

\begin{figure}[htbp]
    \begin{center}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1000.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1000.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.1995.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.1995.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/N_0.9000_0.3981.eps}
	\includegraphics[width=0.45\textwidth]{figs/Cubic/Stream/A_0.9000_0.3981.eps}
        \caption{Streamlines of the flow for various electric field $\beta$ values: 
        numerical results (left) and analytical approximation (right) for
        $\gamma = 0.9$.  The steady-state velocity $\cU$ is positive, so the
        ion-exchanger drifts to the right. 
        Note that there is a good correspondence between the numerical
        results and the analytical solution for $\beta < 1$, validating
        the vortex formation.
        }
    \label{fig:Vortex}
    \end{center}
\end{figure}
